I am among the lucky few to enter graduate school under the exceptional mentorship of Dr. Sheena Josselyn, and it's hard to overstate my gratitude for Sheena's motivation, guidance and advice over my PhD program. Sheena's unwavering encouragement and support gave me the courage to transition from molecular biology to engineering and computational neuroscience with no prior experience, and made the journey extremely fulfilling. Sheena has shown me what an iconic scientist is: knowledgeable yet humble, rigorous yet open-minded, passionate yet meticulous, and these attributes are what I will strive to achieve. I would also like to thank my program advisory committee members: Dr. Junchul Kim, Dr. Christopher Yip and Dr. Fang Liu. Your suggestions and feedback during committee meetings has been very helpful, and greatly pushed the project forward. 

I would like to thank Dr.Paul Frankland for always being helpful and supportive, and providing great new ideas for experiments and analysis. I have been tremendously privileged to work with the brilliant members of the Josselyn \slash{} Frankland lab during the PhD program. I would like to express my gratitude to Dr. Valentina Mercaldo, who volunteered to be the unfortunate pilot user of the bug-ridden mini-microscope prototype and actually endured it --- this work would not exist if not for her unreasonable perseverance and enthusiasm. Furthermore, I would like to thank Alexander Jacob for help with building and refining the mini-microscope design, and Dr. Ying Meng for discussions about Alzheimer's disease and input for this thesis. I would also like to particularly thank Dr. Asim Rashid, with whom I collaborated when I first came to the lab. His guidance and infectious composedness, both towards science and life in general, has made me feel much less stressed in graduate school than I am supposed to be. Besides the Josselyn \slash{} Frankland lab members, I have also received tremendous help from Dr. Nathan Insel and Dr. David Redish. I am grateful for their sharp ideas, deep insights and constructive critiques for the mini-microscope data and analysis. 

This long journey of graduate school is not without exceptional support from my friends and family.  I would like to thank Miao, Xiangyuan, and Mengchen for the many sleepless nights where failures in graduate school were laughed at. I would also like to thank my parents for their unconditional support and encouragement for me to pursue my passion. Last but not the least, I could not have come this far without the tremendous love and support from my wife Wei. Thank you for your understanding and patience, and for making me feel like a giant by keeping my head in the clouds and my feet on the ground. 
