\chapter{Introduction}

How does the mind work? This question has been asked by a human, probably since the first human realized about the existence of a mind. While philosophically, the relationship between the mind and the brain is still debatable, however the development in neuroscience and related fields have significantly shrinked the gap between the mind and the brain, or at least, suggested that understanding the brain is the first step of the understanding the mind, if the two are two separate entities. 

It therefore helps to clarity what does ``understand'' really means. It helps to investigate what other ``understandable'' topics have in common, for example, in other well-developed scientific fields, and established scientific methods. One of the powerful tools we have for science, is abstraction. The human brain, although extremely complicated, unfortunate only has a limited capacity for concious process of knowledge. Only a handful of features can be processed simultaneously, and only basic low-order relationship between these features can be processed. Therefore, to understand the world, which is extremely complex, scientists used the tool of abstraction: when the information for processing gets too much for us to process, we remove some information, and used a minimum to investigate. 

In this sense, ``understanding'' is defined by abstractions. To ``understand'' a subject, we need to create a tower of abstraction, with the object at the bottom, and each level being an abstraction of one level down. Depending on the question asked, we can move freely between the abstraction levels to search for useful knowledge, and use the knowledge to explain and predict the behavior of the object. 

The brain has naturally created these abstractions by physical scale. At the bottom level, molecules interact, and created closed compartments of cells. The cells interact with each other, creating circuits. The circuits computes input and produce output, and generates cognition and behaviour. 



It is a wonder how science is understandable at all. 

It the mechanism underlying the brain abstractable?

Abstraction by structure:
    cellular, circuitry, and functional

Diseased brain


