\chapter{Memory traces in amygdala}

\section{Introduction}

\section{Methods}

\subsection{Animals}
Wildtype C57/BL6 $\times$ 129 F1 mice of 3-month age were used in the experiment. All animals were caged in groups of 4 or 5, with a 12-hour light\slash dark cycle. Food and water are provided \textit{ad libitum} to all animals.

\subsection{Viral vectors}
 p1005 plasmid expresses \gls{gfp} under \gls{cmv} promoter. CREB--p1005--\gls{gfp} plasmid was constructed by inserting \gls{creb} \gls{cdna} into p1005 plasmid, under the control of \gls{hsv} IE4/5 promoter. Plasmids were packaged with a replication-defective \gls{hsv} helper virus as previously described \citep{neve05}. All virus was concentrated by sucrose gradient, diluted in 10\% sucrose and stored in \SI{-80}{\celsius}. A typical titer of the virus is \num{1e7} infectious unit per \si{ml}. 

\subsection{Surgery}
See general methods.\todo{refer to general methods}

\subsection{Auditory fear conditioning}
See general methods.\todo{refer to general methods}

\subsection{\Acrlong{cpp}}

 The \gls{cpp} boxes are composed of two chambers with a removable shutter that can be switched to allow animals to move between the chambers. One chamber has white walls, textured floor and is sprayed with water, the other chamber has striped walls, smooth floor and is sprayed with 2\% acetic acid.\todo{insert cpp image here} Animals were first placed in the box, allowed to travel between two chambers for \SI{10}{\min}, and the amount of time spent in each chamber is recorded as a measure for pre-conditioning preference. During training, animals received saline (\gls{ip}), and confined to one of the chambers for \SI{15}{\min}. In the next day, the animals received cocaine injection (\SI{30}{\mg\per\kg}, \gls{ip}), and paired to the other chamber for \SI{15}{\min}. The animals are kept in home cage for one day and put back to the \gls{cpp} boxes and allowed to move freely between chambers for \SI{10}{\min}. The amount of time spent in each chamber were recorded. The difference in time spent between cocaine and saline conditioned chamber were calculated as cocaine preference.

\subsection{\Acrlong{fish}}
The animals were sacrificed \SI{2}{\hour} after the beginning of the light cycle on the day following the auditory fear conditioning. The brains were quickly dissected, frozen on dry ice, and stored in \SI{-80}{\celsius}. The brains were then sliced into \SI{20}{\um} coronal sections using a cryostat and mounted onto gelatine-coated slides. \Gls{fish} were carried out as previously described \citep{guzowski99}. \gls{dig}-labeled \gls{arc} and \gls{fitc}-labeled \gls{gfp} antisense \gls{rna} probes were prepared and hybridized to the slices overnight. Alexa-488 conjugated anti-\gls{gfp} (1:100) and \gls{hrp}-conjugated anti-\gls{dig} (1:100) antibodies were used to detect hybridized \gls{gfp} and \gls{arc} \gls{rna} probes. The \gls{arc} signals were amplified using \gls{tsa}-biotin kit and visualized by Alexa 568-conjugated streptavidin. The nuclei were counter-stained with Hoechst 33258.

\subsection{Imaging and cell counting}
Images were taken on a laser-scanning microscope. The parameters were optimized for \gls{arc} signal and kept constant across slides. Confocal stacks of 1um were taken by 40x objectives. Small-uniform nuclei from glial cells and nuclei on the top or bottom stacks were excluded from the counting. \gls{arc} and \gls{gfp} transcription foci  were examined for each included nuclei. Total number of cells, \gls{arc} positive cells (\gls{arc}+), \gls{arc} and \gls{gfp} double positive cells (\gls{arc}+/\gls{gfp}+) were counted. \gls{arc} ratio was calculated by dividing \gls{arc}+/\gls{gfp}+ with \gls{gfp}+.

\section{Results}
\section{Discussion}
